PHAT RAID, yo

### 2014-05-13 paper/paper.tex
hdd perf

In a review of hard disk performance \cite{disk-perf}, Hard Disk Drives (HDD) were compared with Solid State Drives (SDD). HDDs use a physical magnetic platter that spins so that a drive head can read or write data by sensing or manipulating the magnetic field in a particular position on to the platter. In contrast, Solid SDD have no moving parts and instead uses integrated circuits as memory to store data persistently. Because the way in which data is accessed is different, the performance characteristics between the two are different.

@@

Figure \ref{fig:hdd-vs-sdd} shows a comparison between read times for a SDD and HDD as a function of position on the disk. HDD storage performance is greatly influenced by where on the disk platter the data was placed. Data can be placed on the outer rim of the platter much more quickly than data placed near the center of the platter as the outer rim is moving faster in comparison (due to conservation of angular momentum). In contrast to HDDs, SDDs do not exhibit this problem as there is no spinning platter. The right diagram in \ref{fig:hdd-vs-sdd} shows relatively constant read performance throughout the entire disk.

\urldef\hwbenchmark\url{http://www.tomshardware.com/charts/ssd-charts-2013/benchmarks%2C129.html}
\begin{figure}
\centering
\begin{tabular}{l || c}
\multicolumn{2}{c}{{\bf Solid State Disk Performance Benchmarks}} \\ \hline
Sequential Write Speed  \hspace{7em} & 55.03 - 481.85 MB/sec \\ 
Write Access Time & 0.03 - 0.32 seconds \\ \hline
Sequential Read Speed &  207.95 - 522.45 MB/sec \\
Read Access Time & 0.03 - 0.22 seconds
\end{tabular}
\caption[Solid State Performance]{Solid State Disk performance for middle 95\% of sold state drives tested in a benchmark. Benchmark available at Benchmark available at \hwbenchmark.}
\label{fig:sdd-perf}
\end{figure}

Figure \ref{fig:sdd-perf} shows the performance for SSDs from a 2013 survey of commercially available SDDs.

>>>>

In a review of hard disk performance \cite{disk-perf}, Hard Disk Drives (HDD) were compared with Solid State Drives (SSD). HDDs use a physical magnetic platter that spins so that a drive head can read or write data by sensing or manipulating the magnetic field in a particular position on to the platter. In contrast, SSDs have no moving parts and instead uses integrated circuits as memory to store data persistently. Because the way in which data is accessed is different, the performance characteristics between the two are different.

@@

Figure \ref{fig:hdd-vs-sdd} shows a comparison between read times for a SSD and HDD as a function of position on the disk. HDD storage performance is greatly influenced by where on the disk platter the data was placed. Data can be placed on the outer rim of the platter much more quickly than data placed near the center of the platter as the outer rim is moving faster in comparison (due to conservation of angular momentum). In contrast to HDDs, SSDs do not exhibit this problem as there is no spinning platter. The right diagram in \ref{fig:hdd-vs-sdd} shows relatively constant read performance throughout the entire disk. Additionally, HDDs have difficultly with random accesses as the drive may need to wait for the drive head to be directly over the correct position on the platter. This problem becomes especially apparent when an individual file is fragmented into multiple blocks by the file system. SSDs have relatively better random access times, in general, though sequential access tends to be many times faster than random access \cite{disk-perf}. HDD performance can also can suffer from {\em spin-up delay}, which happens as a result of a power-saving measure that stops spinning the disk during idle times.

We decided that HDDs have far too much performance variability in order to be properly modeled. As a result, we instead chose to simulate the performance characteristics of SSDs as they have relatively constant access times regardless of sector position on the drive and also do not suffer from {\em spin-up delay}.

\urldef\hwbenchmark\url{http://www.tomshardware.com/charts/ssd-charts-2013/benchmarks%2C129.html}
\begin{figure}
\centering
\begin{tabular}{l || c}
\multicolumn{2}{c}{{\bf Solid State Disk Performance Benchmarks}} \\ \hline
Sequential Write Speed  \hspace{7em} & 55.03 - 481.85 MB/sec \\ 
Write Access Time & 0.03 - 0.32 ms \\ \hline
Sequential Read Speed &  207.95 - 522.45 MB/sec \\
Read Access Time & 0.03 - 0.22 ms
\end{tabular}
\caption[Solid State Performance]{Solid State Disk performance for middle 95\% of sold state drives tested in a benchmark. Benchmark available at Benchmark available at \hwbenchmark.}
\label{fig:sdd-perf}
\end{figure}

Figure \ref{fig:sdd-perf} shows the performance for SSDs from a 2013 survey of commercially available SSDs. Sequential write speeds measure the throughput (in megabytes per second) of data stored on the drive when the data is being written in the drive's natural sequential order (e.g. increasing sectors). Similarly, sequential read speed measures the throughput for sequential reads. Read/Write access times represent the latency of performing a single random read or write.
